Human Pose Estimation for Video Game Control

### 2022-05-09 paper/paper.tex
added graphs for motion tracking
edits, added a gameplay image

\begin{abstract}
    Current methods of interacting with computers are flawed in a 
    couple of key ways: they fail to map physically-intuitive motions to their computer 
    control counterparts, and they rely heavily on a user's fine-motor skills, 
    which are heavily impacted by factors such as muscle coordination disabilities 
    and old age. In this paper, we propose a system of computer control through 
    gesture tracking via real-time human pose estimation on an embedded device, 
    which is capable of addresssing these issues, by mapping general physically-intuitive 
    motions into computer control. Furthermore, our device boasts low latency in 
    the human-computer interaction, and is minimally intrustive to the computer being 
    controlled. We test the viability of our system as a computer-control device by playing two 
    video games using only gestures.
\end{abstract}

@@

\subsubsection{Openpose}
One popular solution to realtime human pose estimation, derived from \cite{8765346}, 
uses Part Affinity Fields (PAFs) to learn to assosciate body parts with individuals in the image, 
and open-source code for the so called openpose library shows promising results for real-time 
human body segmentation.

@@

A number of guides exist for implementing feature tracking over video. \cite{tracking_1} 
and \cite{tracking_2} demonstrate simple object tracking across video frames, and \cite{tracking_2} 
demonstrates a system shown to be accurate with motion of hands. We drew on \cite{tracking_1} and 
\cite{tracking_2} in developing a tracking algorithm for the identification of a human user ducking 
or jumping from a keypoint cloud.

@@

After establishing the midpoint feature, we obtain graphs of the vertical 
position and derivative of vertical position of the midpoint feature over time 
as a user performs jumping and ducking motions in order to develop a game-specific 
classifier for this task. A few methods we considered and our analysis of them 
are given below:

@@

\section{Results}
Once the human pose estimator, keypoint classifiers, and game interface are integrated into 
a single system, we are able to play both of our example games in real time (15+ FPS) through only our 
gestures in front of the camera. Our systems are robust, performing well across a variety of scenarios, 
including when keypoints are missing and erroneous pose estimation. The games are responsive and 
fully playable from only gestural input, demonstrating little to no loss of playability when 
moving from keyboard and mouse input to the gestural command input through our human-computer 
interface device.\\

\section{Conclusion and Future Works}
The goal of this project was to develop a system that can map human gestures through a video 
stream into usable computer command input, replacing how we currently interact with computers 
through keyboards, mice, and joysticks. Furthermore, we aimed to develop a system that 
places little to no computational expense on the computer playing the game. 
Our system demonstrates that we accomplish this goal 
in real time, by playing two example video games using gestural inputs, with computation 
and realtime inference done on an edge device, the NVIDIA Jetson Nano.\\

@@

Other areas of future work that can improve our system and bring it closer to the goal of a 
general purpose human computer interface that can mimic a wider range of commands include more 
general keypoint classifiers using machine learning techniques that can be easily expanded 
to a wider range of commands. In addition, a communication link between the Jetson Nano and 
a gaming device can be implemented, allowing the user to play games on other devices, using our 
human-computer interface only as an intermediate step.

>>>>

\begin{abstract}
    Current methods of interacting with computers are flawed in a 
    couple of key ways, especially when it comes to video games: they fail to map physically-intuitive motions to their computer 
    control counterparts, and they rely heavily on a user's fine-motor skills, 
    which are heavily impacted by factors such as muscle coordination disabilities 
    and old age. In this paper, we propose a system of computer control through 
    gesture tracking via real-time human pose estimation on an embedded device, 
    which is capable of addresssing these issues, by mapping general physically-intuitive 
    motions into computer control. Furthermore, our device boasts low latency in 
    the human-computer interaction, and is minimally intrustive to the computer being 
    controlled. We test the viability of our system as a computer-control device by playing two 
    video games using only gestures.
\end{abstract}

@@

\subsubsection{Openpose}
One popular solution to realtime human pose estimation, derived from \cite{8765346}, 
uses Part Affinity Fields (PAFs) to learn to assosciate body parts with individuals in the image, 
and open-source code for the so called openpose library shows promising results for real-time 
multi-person 2D pose detection, including body, foot, hand, and facial keypoints.

@@

A number of guides exist for implementing feature tracking over video. \cite{tracking_1} 
and \cite{tracking_2} demonstrate simple object tracking across video frames, and \cite{tracking_2} 
demonstrates a system shown to be accurate with motion of hands.This is done by calculating the changes between consecutive frames and finding trends in a window of input data. We drew on \cite{tracking_1} and 
\cite{tracking_2} in developing a tracking algorithm for the identification of a human user ducking 
or jumping from a keypoint cloud.

@@

After establishing the midpoint feature, we obtain graphs of the vertical 
position and derivative of vertical position of the midpoint feature over time 
as a user performs jumping and ducking motions in order to develop a game-specific 
classifier for this task. A few methods we considered and our analysis of them 
are given below.

\begin{figure}[h]
    \centering
    \includegraphics[width = .8\linewidth]{images/center_height.png}
    \includegraphics[width = .8\linewidth]{images/center_deriv.png}
    \caption{Top: y-position of face midpoint over time. Bottom: derivative 
    of y-position of face midpoint over time.}
\end{figure}

@@

\section{Results}
Once the human pose estimator, keypoint classifiers, and game interface are integrated into 
a single system, we are able to play both of our example games in real time (15+ FPS) through only our 
gestures in front of the camera. Our systems are robust, performing well across a variety of scenarios, 
including when keypoints are missing and erroneous pose estimation. The games are responsive and 
fully playable from only gestural input, demonstrating little to no loss of playability when 
moving from keyboard and mouse input to the gestural command input through our human-computer 
interface device.\\
\begin{figure}[h]
    \centering
    \includegraphics[width = .5\linewidth,height=4cm]{images/user.png}\hfill
    \includegraphics[width = .5\linewidth,height=4cm]{images/game.png}
    \caption{Real-time game play using our interface}
\end{figure}
\section{Conclusion and Future Works}
The goal of this project was to develop a system that can map human gestures through a video 
stream into usable computer command input, replacing how we currently interact with computers 
through keyboards, mice, and joysticks. Furthermore, we aimed to develop a system that 
places little to no computational expense on the computer playing the game. 
Our system demonstrates that we accomplish this goal 
in real time, by playing two example video games using gestural inputs, with computation 
and realtime inference done on an edge device, the NVIDIA Jetson Nano.\\

@@

Other areas of future work that can improve our system and bring it closer to the goal of a 
general purpose human computer interface that can mimic a wider range of commands include more 
general keypoint classifiers using machine learning techniques that can be easily expanded 
to a wider range of commands. As an immediate next step, we could develop kepoint classifiers that are specific to a video game genre (such as RPGs or shooters) rather than a sepcific game.
In addition, a communication link between the Jetson Nano and 
a gaming device can be implemented, allowing the user to play games on other devices, using our 
human-computer interface only as an intermediate step.
